KV Analysis for Performing-Dynamics performances

### 2021-02-01 material/expstimuli/analysis/expression/stim_a/duration.Rmd
correct comments and show data by trial
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# Valid performances (exclude Duration outliers)
- Exclude mean Duration outside 3SD

## Legato
```{r outlier_leg, echo = FALSE}
# for legato
excluded_duration_leg <- duration[Subcomponent == "Legato" & Mean < duration_all[Subcomponent == "Legato"]$Mean+3*duration_all[Subcomponent == "Legato"]$SD & Mean > duration_all[Subcomponent == "Legato"]$Mean-3*duration_all$SD]
print(excluded_duration_leg)
```
- The number of excluded performance: `r duration_all[Subcomponent == "Legato"]$N-nrow(excluded_duration_leg)`

## Staccato
```{r outlier_sta, echo = FALSE}
# for staccato
excluded_duration_sta <- duration[Subcomponent == "Staccato" & Mean < duration_all[Subcomponent == "Staccato"]$Mean+3*duration_all[Subcomponent == "Staccato"]$SD & Mean > duration_all$Mean-3*duration_all[Subcomponent == "Staccato"]$SD]
print(excluded_duration_sta)
```
- The number of excluded performance: `r duration_all[Subcomponent == "Staccato"]$N-nrow(excluded_duration_sta)`

>>>>

# Included performances for averaging
## Legato
```{r outlier_leg, echo = FALSE}
# for legato
duration_trial_leg <- dt_duration[Subcomponent == "Legato", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), by = .(SubNr, TrialNr)]
duration_trial_leg
```

## Staccato
```{r outlier_sta, echo = FALSE}
# for staccato
duration_trial_sta <- dt_duration[Subcomponent == "Staccato", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), by = .(SubNr, TrialNr, Subcomponent)]
duration_trial_sta
```

### 2021-02-01 material/expstimuli/analysis/expression/stim_d/kv.Rmd
correct comments and show data by trial
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# Valid performances (exclude KVs outliers)
## Forte
```{r outlier_for, echo = FALSE}
# for forte
excluded_kv_for <- kv[Subcomponent == "Forte" & Mean < kv_all[Subcomponent == "Forte"]$Mean+3*kv_all[Subcomponent == "Forte"]$SD & Mean > kv_all[Subcomponent == "Forte"]$Mean-3*kv_all$SD]
print(excluded_kv_for)
```
- The number of excluded performance: `r kv_all[Subcomponent == "Forte"]$N-nrow(excluded_kv_for)`

## Piano
```{r outlier_pia, echo = FALSE}
# for piano
excluded_kv_pia <- kv[Subcomponent == "Piano" & Mean < kv_all[Subcomponent == "Piano"]$Mean+3*kv_all[Subcomponent == "Piano"]$SD & Mean > kv_all[Subcomponent == "Piano"]$Mean-3*kv_all$SD]
print(excluded_kv_pia)
```
- The number of excluded performance: `r kv_all[Subcomponent == "Piano"]$N-nrow(excluded_kv_pia)`

>>>>

# Included performances for averaging
## Forte
```{r outlier_for, echo = FALSE}
# for forte
kv_trial_for <- dt_kv[Subcomponent == "Forte", .(N = length(Velocity), Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, TrialNr)]
kv_trial_for
```

## Piano
```{r outlier_pia, echo = FALSE}
# for piano
kv_trial_pia <- dt_kv[Subcomponent == "Piano", .(N = length(Velocity), Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, TrialNr)]
kv_trial_pia
```
